---
title: "Learning to See Meaning \\newline in Visual Words and Objects"
author: "Alexander Enge"
institute: "Humboldt-Universität zu Berlin"
date: "07.10.2025"
classoption: "t"
bibliography: "misc/references.bib"
csl: "misc/template/apa.csl"
output:
  beamer_presentation:
    includes:
      in_header: "misc/template/hu_template.tex"
---

```{r, echo=FALSE, message=FALSE}
# Load required packages
library(here)
library(knitr)

# Set global chunk options
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%",
  fig.align = "center"
)

# Helper function to include figures if they exist
include_figure <- function(filename, dir = here("defense/figures"), ...) {
  path <- file.path(dir, filename)
  if (file.exists(path)) include_graphics(here(path), ...)
}
```

## Introduction

* Bla bla blub

## Study 1: The semantic system in children

* 50 fMRI experiments on semantic cognition in children
* *N* = 1,018 participants, mean age 5.5--12.8 years
* 687 peak coordinates (400, left 287 right)

\bigskip

```{r, out.width="100%"}
include_figure("meta_intro.png")
```

\tiny @enge2021

## Study 1: The semantic system in children

```{r, out.width="100%"}
include_figure("meta_acar_2018.png")
```

\tiny @acar2018

## Study 1: The semantic system in children

```{r, out.width="95%"}
include_figure("meta_results.png")
```

## Study 2: Visual semantics in learning to read

* Longitudinal study with 15 children (5--9 years), 6 time points
* 18 month of reading instruction in Hindi/Devanagari
* Standardized reading tests + fMRI

```{r, out.width="93%"}
include_figure("slang_intro.png")
```

\smallskip

## Study 2: Visual semantics in learning to read

* Mini block design fMRI task
* Spoken + written non-words, pseudowords, real words
* Target detection task

\smallskip

```{r, out.width="93%"}
include_figure("slang_task.png")
```

\tiny See @dehaene-lambertz2018

## Study 2: Visual semantics in learning to read

* Longitudinal analysis using linear mixed models (LMMs)
* Whole-brain univariate change in activation strength
* Multivariate change in audio-visual pattern similarity
* Multivariate change in within-condition pattern stability

\bigskip

```{r, out.width="50%"}
include_figure("slang_packages.png")
```

\bigskip

\tiny See @chen2013a; @madhyastha2018
\newline<https://github.com/SkeideLab/SLANG-analysis/blob/SLANG/scripts/univariate.py>

## Study 2: Visual semantics in learning to read

```{r, out.width="100%"}
include_figure("slang_words_vs_baseline.png")
```

\tiny @enge2024

## Study 2: Visual semantics in learning to read

```{r, out.width="100%"}
include_figure("slang_multivariate.png")
```

\tiny @enge2024

## Study 3: Visual semantics in novel objects

```{r, out.width="95%"}
include_figure("aha_design.png")
```

\tiny @enge2023a

## Study 3: Visual semantics in novel objects

```{r, out.width="100%"}
include_figure("aha_results.png")
```

\tiny @enge2023a

## General discussion

* Bla bla blub

## Thank you

```{r, out.width="100%"}
include_figure("thanks.png")
```

## References

\tiny

::: {#refs}
:::

## Study 1: The semantic system in children

```{r, out.width="55%"}
include_figure("meta_prisma.png")
```

## Study 1: The semantic system in children

```{r, out.width="60%"}
include_figure("meta_methods.png")
```

\tiny @enge2021

## Study 1: The semantic system in children

\bigskip

```{r, out.width="100%"}
include_figure("meta_tasks.png")
```

\tiny @enge2021

## Study 2: Visual semantics in learning to read

```{r, out.width="60%"}
include_figure("slang_tests.png")
```

## Study 3: Visual semantics in novel objects

```{r, out.width="80%"}
include_figure("aha_control.png")
```

## Study 3: Visual semantics in novel objects

```{r, out.width="60%"}
include_figure("aha_tfr_insight.png")
```

\tiny @enge2023a

## Study 3: Visual semantics in novel objects

```{r, out.width="60.5%"}
include_figure("aha_tfr_post_insight.png")
```

\tiny @enge2023a
