---
title: "Learning to See Meaning \\newline in Visual Words and Objects"
author: "Alexander Enge"
institute: "Humboldt-Universität zu Berlin"
date: "07.10.2025"
classoption: "t"
bibliography: "misc/references.bib"
csl: "misc/template/apa.csl"
output:
  beamer_presentation:
    includes:
      in_header: "misc/template/hu_template.tex"
---

```{r, echo=FALSE, message=FALSE}
# Load required packages
library(here)
library(knitr)

# Set global chunk options
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%",
  fig.align = "center"
)

# Helper function to include figures if they exist
include_figure <- function(filename, dir = here("defense/figures"), ...) {
  path <- file.path(dir, filename)
  if (file.exists(path)) include_graphics(here(path), ...)
}
```

## Introduction

\vspace{1em}

```{r, out.width="100%"}
include_figure("intro_example_blank.jpg")
```

## Introduction

\vspace{1em}

```{r, out.width="100%"}
include_figure("intro_example.jpg")
```

## Introduction

\vspace{-1.5em}

```{r, out.width="95%"}
include_figure("intro_example_solution.jpg")
```

## Introduction

* Feed-forward visual system for core object recognition
* Semantic system based on object categories, linguistic contrasts, distributional statistics
* **Needs bi-directional interfaces**

\bigskip

```{r, out.width="95%"}
include_figure("intro_brain.jpg")
```

\tiny @binder2009; @deniz2019; @dicarlo2012; @felleman1991; @huth2016

## Introduction

* **Study 1: The semantic system in children**
  \newline &rarr; Meta-analysis of the developing semantic system

* **Study 2: Visual semantics in learning to read**
  \newline &rarr; Longitudinal fMRI study of reading acquisition

* **Study 3: Visual semantics in novel objects**
  \newline &rarr; EEG training study on insight into object function

## Study 1: The semantic system in children

* 50 fMRI experiments on semantic cognition in children
* *N* = 1,018 participants, mean age 5.5--12.8 years
* 687 peak coordinates (400, left 287 right)

\bigskip

```{r, out.width="100%"}
include_figure("meta_intro.jpg")
```

\tiny @enge2021

## Study 1: The semantic system in children

```{r, out.width="100%"}
include_figure("meta_acar_2018.jpg")
```

\tiny @acar2018

## Study 1: The semantic system in children

```{r, out.width="95%"}
include_figure("meta_results.jpg")
```

## Study 2: Visual semantics in learning to read

* Longitudinal study with 15 children (5--9 years), 6 time points
* 18 month of reading instruction in Hindi/Devanagari
* Standardized reading tests + fMRI

```{r, out.width="93%"}
include_figure("slang_intro.jpg")
```

\smallskip

## Study 2: Visual semantics in learning to read

* Mini block design fMRI task
* Spoken + written non-words, pseudowords, real words
* Target detection task

\smallskip

```{r, out.width="93%"}
include_figure("slang_task.jpg")
```

\tiny See @dehaene-lambertz2018

## Study 2: Visual semantics in learning to read

* Longitudinal analysis using linear mixed models (LMMs)
* Whole-brain univariate change in activation strength
* Multivariate change in pattern similarity and stability

\bigskip

```{julia, echo=TRUE, eval=FALSE, out.width="60%"}
using MixedModels
fm = @formula(beta ~ 1 + time + time2 + (1 + time + time2 | subject))
mm = fit(MixedModel, fm, df)
```

\tiny <https://github.com/SkeideLab/SLANG-analysis/blob/SLANG/scripts/univariate.py>
\newline See also @chen2013a; @madhyastha2018

\bigskip

```{r, out.width="50%"}
include_figure("slang_packages.jpg")
```

## Study 2: Visual semantics in learning to read

```{r, out.width="100%"}
include_figure("slang_words_vs_baseline.jpg")
```

\tiny @enge2024a

## Study 2: Visual semantics in learning to read

```{r, out.width="100%"}
include_figure("slang_multivariate.jpg")
```

\tiny @enge2024a

## Study 3: Visual semantics in novel objects

* *N* = 48 adults, 120 unfamiliar objects
* Compare informed vs. uninformed perception in each phase (before, during, after insight)

\smallskip

* **P1 (100--150 ms):** Early visual preprocessing
* **N170 (150--200 ms):** High-level visual preprocessing
* **N400 (400--700 ms):** Semantic processing

\smallskip

* Exploratory time-frequency analysis

\bigskip

\tiny @enge2023a

## Study 3: Visual semantics in novel objects

```{r, out.width="95%"}
include_figure("aha_design.jpg")
```

\tiny @enge2023a

## Study 3: Visual semantics in novel objects

```{r, out.width="100%"}
include_figure("aha_results.jpg")
```

\tiny @enge2023a

## Bonus: `hu-neuro-pipeline` package

\vspace{-1em}

```{r, out.width="100%"}
include_figure("pipeline_overview.jpg")
```

## Bonus: `hu-neuro-pipeline` package

* **Homepage:** [hu-neuro-pipeline.readthedocs.io](https://hu-neuro-pipeline.readthedocs.io)
* **Slides:** [github.com/alexenge/hu-neuro-pipeline-workshop](https://github.com/alexenge/hu-neuro-pipeline-workshop)
* **EEG analysis course:** [alexenge.github.io/intro-to-eeg](https://alexenge.github.io/intro-to-eeg)
* **Speech artifact correction:** [eeg-ride.readthedocs.io](https://eeg-ride.readthedocs.io)

\vspace{10.5em}

\tiny @enge2023a; @fromer2018; @ouyang2015

## Bonus: `hu-neuro-pipeline` package

\vspace{-1.5em}

```{r, out.width="100%"}
include_figure("pipeline_docs_code.png")
```

## Bonus: `hu-neuro-pipeline` package

\vspace{-1.5em}

```{r, out.width="100%"}
include_figure("pipeline_docs_plot.png")
```

## Discussion

1. Semantic system in children largely adult-like by age 10

2. Learning to read increases audio-visual response patterns in left vOT cortex (*)

3. Discovering object function alters visual processing within first 200 ms

## Discussion

* No engagement of semantic areas from meta-analysis in reading study

\smallskip

* Difficult to pinpoint top-down EEG effects anatomically

\smallskip

* Similar mechanisms in learning to read and discovering object function?
  - Both involve linking visual features to meaning and *vice versa*
  - But: incidental vs. diagnostic visual features
  - Phylogenetically and ontogenetically very different

## Discussion

* Limitations:
  - **Meta-analysis:** publication bias, coordinate-based approach
  - **Reading study:** sample size (!!!), intervention strength and duration, experimental design
  - **Object study:** ecological validity, localization/neural mechanisms

## Discussion

* Replicability crisis, power, flexibility in cognitive neuroscience
* Generalizability to real-world tasks and people
* Need for computationally explicit theories
* Better methods can't hurt

\smallskip

```{r, out.width="100%"}
include_figure("discussion_manypipelines.jpg")
```

\tiny See @botvinik-nezer2020; @button2013; @cummins2000; @forscher1963; @marek2022; @opensciencecollaboration2015; @pavlov2021; @scheel2021a; @simmons2011; @szucs2017; @szucs2020; @trubutschek2024; @yarkoni2020

## Thank you

```{r, out.width="100%"}
include_figure("thanks.jpg")
```

## References {.allowframebreaks}

\tiny

::: {#refs}
:::

## Study 1: The semantic system in children

```{r, out.width="55%"}
include_figure("meta_prisma.jpg")
```

## Study 1: The semantic system in children

```{r, out.width="60%"}
include_figure("meta_methods.jpg")
```

\tiny @enge2021

## Study 1: The semantic system in children

\bigskip

```{r, out.width="100%"}
include_figure("meta_tasks.jpg")
```

\tiny @enge2021

## Study 2: Visual semantics in learning to read

```{r, out.width="60%"}
include_figure("slang_tests.jpg")
```

## Study 3: Visual semantics in novel objects

```{r, out.width="80%"}
include_figure("aha_control.jpg")
```

## Study 3: Visual semantics in novel objects

```{r, out.width="60%"}
include_figure("aha_tfr_insight.jpg")
```

\tiny @enge2023a

## Study 3: Visual semantics in novel objects

```{r, out.width="60.5%"}
include_figure("aha_tfr_post_insight.jpg")
```

\tiny @enge2023a

## Bonus: `hu-neuro-pipeline` package

```{r, echo=TRUE, eval=FALSE}
# Load packages
library("reticulate")
pipeline <- import("pipeline")

# Download example data
ucap_files <- pipeline$datasets$get_ucap()

# Run the pipeline
res <- pipeline$group_pipeline(
  raw_files = ucap_files$raw_files,
  log_files = ucap_files$log_files,
  besa_files = ucap_files$besa_files,
  output_dir = "output",
  triggers = c(201:208, 211:218),
  components = list(
    "name" = list("N2", "P3b"),
    "tmin" = list(0.25, 0.4),
    "tmax" = list(0.35, 0.55),
    "roi" = list(
      c("FC1", "FC2", "C1", "C2", "Cz"),
      c("CP3", "CP1", "CPz", "CP2", "CP4", "P3", "Pz", "P4", "PO3", "POz", "PO4")
    )
  ),
  average_by = list(blurr = "n_b == 'blurr'", normal = "n_b == 'normal'")
)
```

## Discussion

```{r, out.width="80%"}
include_figure("discussion_chinese.jpg")
```

## Discussion

```{r, out.width="100%"}
include_figure("discussion_memes.jpg")
```

\tiny <https://jamesheathers.medium.com/i-quit-be062295f638>
\newline <https://slimemoldtimemold.com>
