---
title: "Learning to See Meaning \\newline in Visual Words and Objects"
author: "Alexander Enge"
institute: "Humboldt-Universität zu Berlin"
date: 2025-XX-XX
classoption: "t"
bibliography: "misc/references.bib"
csl: "misc/template/apa.csl"
output:
  beamer_presentation:
    includes:
      in_header: "misc/template/hu_template.tex"
---

```{r, echo=FALSE, message=FALSE}
# Load required packages
library(here)
library(knitr)

# Set global chunk options
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%",
  fig.align = "center"
)

# Helper function to include figures if they exist

include_figure <- function(filename, dir = here("defense/figures"), ...) {
  path <- file.path(dir, filename)
  if (file.exists(path)) include_graphics(here(path), ...)
}
```

## Introduction

## Study 1: The Semantic System in Children

* 50 fMRI experiments on semantic cognition in children
* *N* = 1,018 participants, mean age 5.5--12.8 years
* 687 peak coordinates (400, left 287 right)

\bigskip

```{r, out.width="100%"}
include_figure("meta_intro.png")
```

\tiny @enge2021

## Study 1: The Semantic System in Children

```{r, out.width="100%"}
include_figure("meta_acar_2018.png")
```

\tiny @acar2018

## Study 1: The Semantic System in Children

```{r, out.width="95%"}
include_figure("meta_results.png")
```

## Thanks

## References

\tiny

::: {#refs}
:::

## Study 1: The Semantic System in Children

```{r, out.width="55%"}
include_figure("meta_prisma.png")
```

## Study 1: The Semantic System in Children

```{r, out.width="60%"}
include_figure("meta_methods.png")
```

\tiny @enge2021

## Study 1: The Semantic System in Children

\bigskip

```{r, out.width="100%"}
include_figure("meta_tasks.png")
```

\tiny @enge2021
